Outbreak Threshold Detection

### 2023-08-29 notebooks/Julia/simulation-detection.qmd

```{julia}
tmax = 10.0
δt = 0.1/365
tspan = (0.0, tmax)
tlength = length(tspan[1]:δt:tspan[2])
Random.seed!(1234);

@@

```{julia}
function run_sir_sim(; init_states, tspan, p)
    prob = DiscreteProblem(init_states, tspan, p)
    jump_prob = JumpProblem(
        prob, Coevolve(), gillespie_jumps..., save_positions = (false, false);
        dep_graph
        )
    jump_sol = solve(jump_prob, SSAStepper(), saveat = δt)
    return jump_sol;
end
```

>>>>

```{julia}
tmax = 10.0
tstep = 0.1/365
tspan = (0.0, tmax)
tlength = length(tspan[1]:tstep:tspan[2])
Random.seed!(1234);

@@

```{julia}
function run_sir_sim(; init_states, tspan, p)
    prob = DiscreteProblem(init_states, tspan, p)
    jump_prob = JumpProblem(
        prob, Coevolve(), gillespie_jumps..., save_positions = (false, false);
        dep_graph
        )
    jump_sol = solve(jump_prob, SSAStepper(), saveat = tstep)
    return jump_sol;
end
```
